Efficient Constructions of Prefer-Max Sequences and of Infinite de Bruijn Sequences

### 2017-01-08 paper.tex
...

	For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that
	$w_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$
	letters suffix of $w$. 
	Because $0$ is the smallest symbol in our alphabet, we get that it is added
	only if all the other symbols cannot be added, i.e., when adding other symbols
	would generate a substring that has already being seen before. 
	Since $w$ comes, as a window, right before some $w[2..m]\tau$,
	we have that $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is
	after $w$. Similar arguments give us that $w[2..m]0$ appears before $w[3..m]0^2$ and
	so on. Together we get that $j_1 < j_2 < \cdots < j_n$. Note that $w_{j_1}=w$, 
	i.e, that $w$ appears as a substring at the $j_1$'s symbol of the
	sequence.

	We will now show that if $w$ contains the symbol $k-1$ it must appear as a
	substring before the $i_0$'s symbol in the sequence. Consider first the case
	where the last (right-most) symbol of $w$ is $k-1$. In this case, $j_n=i_{0}-1$
	so we have, because $j_1 < j_n$, that $w$ appears as a substring before the
	$i_0$'th symbol in the sequence. The second case is when the last (right-most)
	symbol in $w$ is not $k-1$ but there is another letter in $w$ which is $k-1$. In
	this case we have that $w$ appears less than $n$ steps after a window that ends
	with $k-1$ and the window $w_{i_0-1}=(k-1)0^{n-1}$ does not
	appear in the windows between them because they all contain $k-1$ at a letter
	that is not  their first. 
	Formally, we have that there is some $m<n$ such that 
	$j_1-m < i_0$,  $w \in \{w_{{j_1}-m},\dots,w_{j_1-1}\}$ and 
	$w_{i_0-1} \notin \{w_{{j_1}-m},\dots,w_{j_1-1}\}$. This gives us that, also in this 
	case, the window $w$ appears before	the index $i_0$.

>>>>

	For $w \in \{0,\dots,k-1\}^n$ and $1 \leq m \leq n$, let $j_m$ be such that
	$w_{j_m} = w[m..n]0^{m-1}$, where $w[m..n]$ is the $n-m+1$
	letters suffix of $w$. 
	Because zero is the smallest symbol in our alphabet, we get that it is added by the prefer-max rule
	only if all the other symbols cannot be added, i.e., when adding other symbols
	would generate a substring that has already being seen before. 
	Since $w$ comes, as a window, right before a word of the form $w[2..m]\tau$ for some $\tau \geq 0$,
	we have that $w[2..m]0$ comes after (or is equal to) $w[2..m]\tau$ which is
	after $w$. Similar arguments give us that $w[2..m]0$ appears before $w[3..m]0^2$ which appears before $w[4..m]0^3$ and
	so on. Together we get that $j_1 < j_2 < \cdots < j_n$. Note that $w_{j_1}=w$, 
	i.e, that $w$ appears as a substring at the $j_1$'s symbol of the
	sequence.

	We will now show that if $w$ contains the symbol $k-1$ it must appear as a
	substring before the $i_0$'s symbol in the sequence, i.e., that $j_1 < i_0$. Consider first the case
	where the last (right-most) symbol of $w$ is $k-1$. In this case, $j_n=i_{0}-1$
	so we have, because $j_1 < j_n$, that $w$ appears as a substring before the
	$i_0$'th symbol in the sequence. The second case is when the last (right-most)
	symbol in $w$ is not $k-1$ but there is another letter in $w$ which is $k-1$. In
	this case we have that $w$ appears less than $n$ steps after a window that ends
	with $k-1$ and the window $w_{i_0-1}=(k-1)0^{n-1}$ does not
	appear in the windows between them because they all contain $k-1$ at a letter
	that is not  their first. 
	Formally, we have that there is some $m<n$ such that 
	$j_1-m < i_0$,  $w \in \{w_{{j_1}-m},\dots,w_{j_1-1}\}$ and 
	$w_{i_0-1} \notin \{w_{{j_1}-m},\dots,w_{j_1-1}\}$. This gives us that, also in this 
	case, the window $w$ appears before	the index $i_0$.
